Extended Data

### 2021-10-18 doc/manuscript/Dow_manuscript_Nature.Rmd
added tree-ring chronology references

The tree-ring records from our focal sites were complemented with a much larger collection spanning `r n_cores_sites-2` deciduous and mixed forest sites in Eastern North America[@maxwell_sampling_2020;@dorangeville_drought_2018; @maxwell_increased_2017] (**Strange et al. 2019 (QUAL); Au et al. 2020 (ACSA); LeBlanc et al Accepted (LITU) ; Maxwell et al. 2020 (QUAL) ; Matheus and Maxwell 2018 ; Schmidt 2015 (Thesis), Maxwell et al. (2020); Maxwell and Harley 2017; Wilde and Maxwell 2018; Maxwell et al. 2019; Maxwell et al. 2015** --- *if someone can give all the DOIs, KAT can easily add to .bib file*). 
Again, species were limited to broadleaf deciduous species with clearly defined xylem porosity (*i.e.*, excluding semi-ring porous).

>>>>

The tree-ring records from our focal sites were complemented with a much larger collection spanning `r n_cores_sites-2` deciduous and mixed forest sites in Eastern North America[@maxwell_sampling_2020;@dorangeville_drought_2018; @maxwell_increased_2017; @wilde_comparing_2018;@strange_comparing_2019;@au_demographic_2020;@matheus_placing_2018;@leblanc_radial_2020;@maxwell_higher_2019;@maxwell_dendroclimatic_2015;@schmidt_325year_2015] (**JUSTIN, please confirm that we got all the appropriate references here.**). 
Again, species were limited to broadleaf deciduous species with clearly defined xylem porosity (*i.e.*, excluding semi-ring porous).
